$jk$-means tests

### 2016-08-29 Rmd/bigKtest.Rmd

set.seed(49)
(mux <- sort(sample(-20:20, 10)))
(muy <- sample(-20:20, 10))

@@

options: 
max iteration=100
convergence error tolerance = 1E-8
```{r}
K <- k
j <- 5

>>>>

set.seed(49)
mux <- sort(sample(-20:20, 10))
muy <- sample(-20:20, 10)

@@

options: 
max iteration=100
convergence error tolerance = 1E-8
```{r}
K <- k
j <- 2
